Individual heterogeneity in the functional topography of the DMN in medial prefrontal cortex 

### 2019-01-25 Manuscript.Rmd
Reshaping the manuscript so that thresholded maps play a big role

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey^1^ & Joseph T. McGuire^1^"
output:
  pdf_document: default
  word_document: 
    reference_docx: Style_reference.docx
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation [@Bartra2013] and DMN [@Laird2009]. Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena [@DelaVega2016]. More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC [@Acikalin2017]. These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system. However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area [@Kragel2018]. While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data. Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject. However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013] and inter-subject functional variability [@Mueller2013a] compared to the rest of the brain, thus making group-averaging studies difficult to interpret.

@@

  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments [@Logothetis]. As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017]. A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics [@Bassett2018a]. From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures [@Garcia2017]. Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016]. Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups [@Garcia2017]. However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning (SP) a more valuable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix). The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e. the Fiedler vector) provides values to divide the network into a positive and a negative community [@Fiedler1975; @Belkin2003]. SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018]. This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.

  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. This description will allow researchers to generate more precise topographic targets for future studies of decision making. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas [@Glasser2016]. We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning. The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects. Finally, we show some interesting properties of SP related to the stability of brain networks.

@@

We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation [@Bartra2013] (n = 27 studies) and DMN [@Laird2009] (n = 77). These represent the surviving areas post-statistical thresholding from each study. For each peak volumetric coordinate, 10 mm sphere masks were generated and then projected to a standard cortical mesh (fs_average, 32,000 vertices) using FreeSurfer. The sphere sections that overlapped with the cortex (should I add the details of the overlap?) were mapped to an atlas of the human cortical surface (360 regions)[@Glasser2016]. This produced a list of standardized parcels that were reported on each study.

With these lists, we identified the areas that were more consistently shared between DMN and valuation. For each literature, we summed the number of times each parcel was reported across studies, and performed a one-way chi-squared test of proportions on each parcel with a null probability equivalent to the bootstrapped (5000 iterations) mean of each literature's report counts. In other words, we checked which regions were significantly (p < 0.05) more reported in their respective literatures than their counterparts. Regions of interest were then determined based on which of the remaining regions were common across literatures.

Next, we identified areas that were solely related to either literature. We limited the search space to the parcels that were contained within the DMN parcellation defined by Yeo et al. [-@Yeo2011]. We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a area-wise chi-squared test of proportions on the number of permuted studies that had reported each area. This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.

@@

In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP) [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). Four resting state sessions (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) were each comprised of 1200 TRs for a total scan time of 14 min 33 s, with left-right and left-right phase encoding implemented on each day. We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).

@@

To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,081 per subject) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we applied Fisher's r to z transformation, and took the exponential of these values so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05). As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Evaluation for more details).

@@

Communities (i.e. clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2003]. First, each adjusted network was represented as an $n$ x $n$ correlation matrix (where $n$ = number of vertices within the ROIs, 5,319). This matrix was then transformed into its normalized Laplacian form

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlations with every other vertex), and $W$ is the correlation matrix. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler Vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975]. Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects). Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].

In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization using the algorithm from Clauset et al. [-@Clauset2004]. This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combination of vertices, and selects the clustering that maximizes the network's modularity. Thus, unlike SP, modularity can fractionate a network into many functional groups. If the partitions from the bounded and unbounded methods show high level of agreement, we can gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.

@@

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns. Modularity and SP show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018]. Their alignment would thus give us confidence in the validity of the resulting topologies. Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group. We then estimate the level of agreement between scans taken across days (i.e. pairs of daily left-right and right-left phase encoding sessions). If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement for the same subject across days than either day compared to every other subject. We then extend this idea by computing the overall agreement across all sessions. Similarly, we expect that sessions within subject will show higher agreement than between subjects. Finally, we perform a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37) 8) comparing each window's functional pattern against the clustering derived from the whole subject's data. This approach should give us a sense of the dynamics of the functional organization of mPFC during rest. We complement this analysis by calculating the proportion of times each surface vertex was affiliated with the DMN community across time, as well as computing the flexibility of each node (i.e. the number of times each vertex changed affiliation across time). Given that the functional heterogeneity of brain areas is unevenly distributed across the brain [@Mueller2013a], we also performed these comparisons for PCC and mPFC separately. Given what we know about these general regions, we expected PCC to be well aligned across participants, and stable within subjects. On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject. We compared the agreement within subjects against across subjects by computing the ratio of the mean RI within and between subjects. Ratios close to one denote good alignment across subjects, while ratios significantly higher than one suggest that partitions per subject were more stable than what you would expect against every other subject.

Given the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we tested the association of their absolute magnitude with the proportion of times a vertex was part of the DMN community during the sliding window analysis. To do this, we performed a mixed effects logistic regression model in which each subject's eigenmap values were used as random predictors of the proportion of times they participated in the DMN community.

@@

BOLD signal recording through fMRI in mPFC in general, and vmPFC in particular, suffers from technical issues that promote signal dropout [@Logothetis]. It was thus important to quantify the potential influence of noise in our findings. We examined this through two complementary steps. First, we computed the temporal signal-to-noise ratio (tSNR) of all the vertices in the ROIs from HCP minimally preprocessed data (i.e. prior to the complementary denoising described in the "fMRI Data" section). We compared the mean tSNR for each region across subjects through a permutation analysis (all permutation analyses involved 5000 iterations). In addition, we compared the mean tSNR between mPFC and PCC through a permutation analysis for each separate subject, and report the percentage of subjects who had a significantly lower mean tSNR in mPFC after FDR correction for multiple testing [@Benjamini2001]. Next, we estimated which vertices within mPFC had a stronger relationship to the overall dynamics of DMN. To do this, we computed the mean time series of each subject's estimated DMN map, which was then predicted by the time series each mPFC vertex in a mass univariate analysis. The resulting $R^2$ values from each model were extracted to determine the total variance of the mean DMN time series explained by each individual vertex. If high noise in more ventral mPFC areas is affecting our results, we should see a gradient of $R^2$ values that decreases ventrally across subjects. We then spatially correlated (Pearson) the $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices. *(PERONSAL NOTE: THIS IS NOW DONE BY CONCATENATING ALL SUBJECTS. IT WOULD PERHAPS BE BETTER TO DO A MIXED EFFECTS MODEL WITH SUBJECTS AS RANDOM EFFECTS, AND TSNR AS A FIXED ONE)*

@@

We performed a coordinate-based meta-analysis to limit the network search space to a set of overlapping and unique standard regions across DMN and SV literatures (see Methods). Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study. Using each literature's mean number of reports per area as the null probability (DMN = `r BD`, 95% CI [`r BDquant`]; SV = `r BV`, 95% CI [`r BVquant`]), one-way chi-squared tests of proportions were performed to identify regions that were significantly present in their respective literatures. The resulting lists were used to identify the set of common brain areas. Unique areas were then determined by permuting the affiliation of each study (i.e. DMN or SV) to create a null distribution of chi-squared statistics, which as used to identify regions more often reported in either literature. Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.

Figure 1 shows the resulting ROIs from these analyses. DMN included `r length(t2)` significant regions, while SV was comprised of `r length(t1)` (see Supplemental Table 1). As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all*p*< 0.05). A region in visual cortex (V2) was also significant, but was removed due to its know unrelated function. Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, *p* < 0.001).

@@

Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning. This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the ROIs Since this is a data-driven approach, there is no a priori labeling for these communities. We thus defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (7m), and ensured that the binary labeling of the vertices was consistent across subjects. In general, the resulting pattern shows large DMN coverage in PCC, with non-DMN vertices populating its anterior segment. mPFC, on the other hand, is mostly covered by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them. This non-DMN section extends posteriorly onto pregenual cinglate cortex. Note that vmPFC does not encompass area a25, which is often related to negative emotional valuation [@Joyce2018]. Interstingly, this topographical combination of dorsal and ventral mPFC, with extensive PCC coverage, matches previous meta-analytic patterns more closely attributed to social cognition than SV [@Hiser2018].

@@

The distribution suggests that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`). The importance of this result lies in that while spectral partitioning forces a bipartition of the network, modularity does not. This adds evidence to the division of these areas into DMN and non-DMN during rest.

>>>>

---
title: 'Individual heterogeneity in the functional topography of the DMN in medial prefrontal cortex '
author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
output:
  pdf_document: default
  word_document: 
    reference_docx: Style_reference.docx
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation [@Bartra2013] and DMN [@Laird2009]. Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena [@DelaVega2016]. More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC [@Acikalin2017]. These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same neural system. However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area [@Kragel2018]. While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data. Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject. However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding [@Zilles2013] and inter-subject functional variability [@Mueller2013a], thus making group-averaging studies difficult to interpret.

@@

  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments [@Logothetis]. As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity [@Gordon2017; @Laumann2015; @Tobyne2017]. A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics [@Bassett2018a]. From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures [@Garcia2017]. Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network [@Fortunato2016]. Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups [@Garcia2017]. However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning (SP) a more valuable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix). The resulting eigenvector corresponding to the second-lowest eigenvalue (i.e. the Fiedler vector) provides values to divide the network into a positive and a negative community [@Fiedler1975; @Belkin2003]. SP has recently been used to characterize the posterior-anterior functional gradient of the insula using rsfMRI data [@Tian2018]. This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.

  In this study, we aimed to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas [@Glasser2016]. We then produce a rsFC networks of all the surface vertices within these ROIs for each of 100 individual resting state dataset from the Human Connectome Project (HCP)[@VanEssen2012], and estimate the extent of DMN coverage through spectral partitioning. Our results suggest the intrinsic functional topography of mPFC and PCC can be reliably partitioned into at least two idiosyncratically arranged networks that can be obscured when averaged across subjects. These sub-networks resembled an organizational scheme recently observed in a handful of subjects (Braga & Buckner, 2017). We also show that graph theoretic tools are capable of identifying these sub-networks in isolated individuals. Our work highlights the usefulness of estimating brain effects at the individual level in these regions, and points to limitations of aggregative methods in determining the degree of neural overlap between DMN and valuation.

@@

We used data from metan-alyses that gathered peak brain coordinates of activity from studies of valuation [@Bartra2013] (n = 27 studies) and DMN [@Laird2009] (n = 77). These represent the surviving areas post-statistical thresholding from each study. For each study, each peak volumetric coordinate was mapped onto a 1mm standard space (MNI152) using AFNI's 3dcalc (CITATION). We then generated 10mm speheres at these points with FSL's fslmaths (CITATION), and then projected to a standard cortical mesh (fs_average, 32,000 vertices, projfrac-max from 0 to 1 by 0.25) using FreeSurfer's mri_vol2surf (CITATION). The sphere sections that overlapped with the cortex were mapped to an atlas of the human cortical surface (360 regions)[@Glasser2016]. This produced a list of standardized parcels that were reported on each study.

<!-- 
With these lists, we identified the areas that were more consistently shared between DMN and valuation. For each literature, we summed the number of times each parcel was reported across studies, and performed a one-way chi-squared test of proportions on each parcel with a null probability equivalent to the bootstrapped (5000 iterations) mean of each literature's report counts. In other words, we checked which regions were significantly (p < 0.05) more reported in their respective literatures than their counterparts. Regions of interest were then determined based on which of the remaining regions were common across literatures.
-->

With these lists, we identified areas that were significantly more associated to either literature. We limited the search space to the parcels that were contained within the medial portion of the DMN parcellation defined by Yeo et al. [-@Yeo2011], as it broadly encompassed our a priori domain of interest. We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum resulting statistic from chi-squared tests of proportions that compared the number of studies that contained each area. This gave us a null distribution of 5000 chi-squared values. We then used the 95th percentile of this distribution as a significance threshold to evaluate the chi-squared values produced by comparing the actual rates of reporting of each area between literatures. The resulting ROIs contained two spatially discontiguous regions (Figure 1), which we label PCC and mPFC for further analyses.

@@

In order to quantify the resting connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project [@VanEssen2012] Q6 release (n = `r nSubj`, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). Four resting state sessions (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) were each comprised of 1200 TRs for a total scan time of 14 min 33 s, with left-right and left-right phase encoding implemented on each day. We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).

@@

To establish each subject's network, we selected all the vertices contained within the ROIs (n = 5,081 per subject) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we applied Fisher's r to z transformation, and took the exponential of these values so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05). As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).

@@

Communities (i.e. clusters) were identified by means of spectral partitioning [@Fiedler1975; @Belkin2003]. First, each network was represented as an $n$ x $n$ matrix of previously adjusted correlation values (where $n$ = number of vertices within the ROIs, 5,319). This matrix was then transformed into its normalized Laplacian form

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlations with every other vertex), and $W$ is the adjusted correlation matrix. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975]. Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community as the one containing the DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects). Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].

In order to evaluate the validity of the resulting partitions, we also estimated these communities using the more traditional approach of modularity maximization, based on the algorithm from Clauset et al. [-@Clauset2004]. This method maximizes a quality function that compares the strength of the connection between any two vertices against a null model of their probability of being randomly connected to any other vertex in the network. The method heuristically iterates through many possible combinations of vertices, and selects the clustering that maximizes the network's modularity. Thus, unlike SP, modularity can fractionate a network into many functional groups. If the partitions from the bounded and unbounded community detection methods show high level of agreement, we can gain confidence in that we are indeed fractioning the ROIs into those belonging to DMN and not.

@@

We performed a number of comparisons among partitions. First, we computed the degree of agreement between SP and modularity per subject to validate the resulting functional patterns. Modularity and SP show overfitting and underfitting tendencies, respectively, in their community detection performance in a diverse number of network types [@Ghasemian2018]. Their alignment would thus give us confidence in the validity of the resulting topologies. Next, we compared the functional organization derived from the whole time series among all subjects, and report the mean RI for the group. We then performed the same evaluation for PCC and mPFC separately, and examined whether there are mean differences in overall agreement within these regions by performing a paired permutation analysis (5000 iterations) on all pairwise RI comparisons across subjects. Given that the functional heterogeneity of brain areas is unevenly distributed across the cortex [@Mueller2013a], we perform the following analyses on PCC and mPFC separately.

To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting organization against the clustering derived from the whole subject's data. Given the high degree of overlap across adjacent windows, we attribute a vertex's tendency to persistently shift allegiances to noise. In that regard, and consdiering the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we also examined the relationship between the magnitude of Fiedler vector values with the proportion of times a vertex was part of the DMN community across windows. To do this, we performed a mixed effects logistic regression model, with subject as a mixed effect and vertex-wise eigenmap values (derived from their full dataset) as fixed predictors on the proportion of times each vertex participated in the DMN community. Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time. These thresholds allowed us to produce individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise.

We then estimated the level of agreement between scans taken across days (i.e. pairs of daily left-right and right-left phase encoding sessions). If the functional organization estimated by SP is indeed subject-specific, we should see higher agreement for the same subject across days than either day compared to every other subject. We tested this idea by computing the ratio of the mean RI within and between subjects. Ratios close to one denoted good alignment across subjects, while ratios significantly higher than one suggested that partitions per subject were more stable than what you would expect against every other subject. We then extend this idea by computing the overall agreement across all sessions. Similar to the day-to-day analysis, we expect that sessions within subjects will show higher agreement than between subjects. Given what we know about these general regions, we expected PCC to be well aligned across participants, and stable within subjects. On the other hand, we hypothesized low agreement of mPFC partitions across participants, but with considerable stability across days and sessions within subject.

@@

BOLD signal recording through fMRI in mPFC in general, and vmPFC in particular, suffers from technical issues that promote signal dropout [@Logothetis]. It was thus important to quantify the potential influence of noise in our findings. We examined this through two complementary steps. First, we computed the temporal signal-to-noise ratio (tSNR) of all the vertices in the ROIs from HCP minimally preprocessed data (i.e. prior to the complementary denoising described in the "fMRI Data" section). We compared the mean tSNR for each region across subjects through a permutation analysis (all permutation analyses involved 5000 iterations). In addition, we compared the mean tSNR between mPFC and PCC through a permutation analysis for each separate subject, and report the percentage of subjects who had a significantly lower mean tSNR in mPFC after FDR correction for multiple testing [@Benjamini2001]. Next, we estimated which vertices within mPFC had a stronger relationship to the overall dynamics of DMN. To do this, we computed the mean time series of each subject's estimated DMN map, which was then predicted by the time series each mPFC vertex in a mass univariate analysis. The resulting $R^2$ values from each model were extracted to determine the total variance of the mean DMN time series explained by each individual vertex. If high noise in more ventral mPFC areas is affecting our results, we should see a gradient of $R^2$ values that decreases ventrally across subjects. We then spatially correlated (Pearson) the $R^2$ and tSNR values to determine whether low tSNR negatively impacted the individual contribution among vertices.

@@

We performed a coordinate-based meta-analysis to identify unique standard regions across DMN and SV literatures (see Methods). Volumetric coordinates from a set of DMN and SV studies were projected onto a cortical surface, and mapped to a multimodal cortical parcellation [@Glasser2016] to produce a list of brain areas reported per study. The areas considered were limited to the medial portion of the DMN, as defined by Yeo et al.[-@Yeo2011]. Unique areas were identified by permuting the affiliation of each study (i.e. DMN or SV) to create a null distribution of chi-squared statistics, which was used to identify regions more often reported in either literature. Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.
Figure 1 shows the resulting ROIs from these analyses. Area 7m was the only one to show unique affiliation, which was significant for DMN ($\chi^2$ = 9.12, *p* < 0.001).

<!--
Using each literature's mean number of reports per area as the null probability (DMN = `r BD`, 95% CI [`r BDquant`]; SV = `r BV`, 95% CI [`r BVquant`]), one-way chi-squared tests of proportions were performed to identify regions that were significantly present in their respective literatures. The resulting lists were used to identify the set of common brain areas. Unique areas were then determined by permuting the affiliation of each study (i.e. DMN or SV) to create a null distribution of chi-squared statistics, which as used to identify regions more often reported in either literature. Importantly, we chose to examine these areas bilaterally, even if their significance was present in only one hemisphere.
DMN included `r length(t2)` significant regions, while SV was comprised of `r length(t1)` (see Supplemental Table 1). As expected, overlapping areas included 15 bilateral regions in PCC (31a, 31pv, RSC, d23ab) and mPFC (9m, 10r, 10v, OFC, a24, d32, p24, p32, s32), as well as a region in IPL (PF) and TPJ (PGi) (all*p*< 0.05). A region in visual cortex (V2) was also significant, but was removed due to its know unrelated function.
-->

@@

Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning. This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the ROIs. Since this is a data-driven approach, there is no a priori labeling for these communities. We thus defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (7m), and ensured that the binary labeling of the vertices was consistent across subjects. In general, the resulting pattern shows large DMN coverage in PCC, with non-DMN vertices populating its anterior segment. mPFC, on the other hand, is mostly covered by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them. This non-DMN section extends posteriorly onto pregenual cinglate cortex. Note that vmPFC does not encompass area a25, which is often related to negative emotional valuation [@Joyce2018]. Interstingly, this topographical combination of dorsal and ventral mPFC, with extensive PCC coverage, matches previous meta-analytic patterns more closely attributed to social cognition than SV [@Hiser2018].

@@

This comparison showed that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`). The importance of this result lies in that while spectral partitioning forces a bipartition of the network, modularity does not. This adds evidence to the division of these areas into DMN and non-DMN during rest.
